### 2023-10-25 manuscript.tex
Moved root PCA figure to supplement

The first two principal components of the root distributions show little overall structure, though there is a slight enrichment of regions along two axes that correlate with acidic and polar features, respectively (Fig.~\ref{fig:root}). Likewise, the projections of the rates onto the first two components are largely distributed along the first principal component (Fig.~\ref{fig:rate}A). This and the variable amounts of sequence divergence in the regions led us to suspect the first principal component was a measure of the overall rate of sequence evolution. Plotting the first principal component against the sum of the average amino acid and indel rates as measured by substitution models revealed a strong association (Fig.~\ref{fig:rate}B). We then projected the rates along second and third principal components to determine if these higher order components contained any additional structure. The resulting distribution is roughly triangular and contains three major axes of variation, corresponding to rapid changes in the regions' proportions of acidic, glutamine, and glycine residues (Fig.~\ref{fig:rate}C-D). Inspection of regions selected along these axes confirmed the high rates of evolution of these features (Fig.~\ref{fig:rate}E-G). Furthermore, we observe a similar distribution when the rates of the order regions were projected along their second and third principal components, which suggests a lack of constraint along these axes is a general property of rapidly evolving proteins (Fig.~\ref{sfig:order}).

@@

\begin{figure}[h!]
\includegraphics[width=\textwidth]{brownian/out/root.png}
\centering
\caption{\textbf{PCA of disorder regions' feature roots.}
\textbf{(A)} The first two PCs of the disorder regions' feature root distributions. The explained variance percentage of each component is indicated in parentheses in the axis labels. \textbf{(B)} The same plot as panel A with the projections of original variables onto the components shown as arrows. Only the 16 features with the largest projections are shown. Scaling of the arrows is arbitrary.}
\label{fig:root}
\end{figure}

>>>>

The first two principal components of the root distributions show little overall structure, though there is a slight enrichment of regions along two axes that correlate with acidic and polar features, respectively (Fig.~\ref{sfig:root}). Likewise, the projections of the rates onto the first two components are largely distributed along the first principal component (Fig.~\ref{fig:rate}A). This and the variable amounts of sequence divergence in the regions led us to suspect the first principal component was a measure of the overall rate of sequence evolution. Plotting the first principal component against the sum of the average amino acid and indel rates as measured by substitution models revealed a strong association (Fig.~\ref{fig:rate}B). We then projected the rates along second and third principal components to determine if these higher order components contained any additional structure. The resulting distribution is roughly triangular and contains three major axes of variation, corresponding to rapid changes in the regions' proportions of acidic, glutamine, and glycine residues (Fig.~\ref{fig:rate}C-D). Inspection of regions selected along these axes confirmed the high rates of evolution of these features (Fig.~\ref{fig:rate}E-G). Furthermore, we observe a similar distribution when the rates of the order regions were projected along their second and third principal components, which suggests a lack of constraint along these axes is a general property of rapidly evolving proteins (Fig.~\ref{sfig:order}).

@@

### 2023-10-25 supporting.tex
Added chi-squared test
Moved root PCA figure to supplement

\begin{figure}[h!]
\includegraphics[width=\textwidth]{pfam/out/pfam.png}
\centering
\caption{\textbf{Overlap of disorder and order regions with Pfam domains.}
\textbf{(A)} Number of disorder and order regions with zero and non-zero overlap with any Pfam domain. \textbf{(B)} Histogram of the disorder and order regions' overlaps with any Pfam domain. Regions with zero overlap are excluded to more clearly show the distribution.}
\label{sfig:pfam}
\end{figure}

@@

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{pfam/out/pfam.png}
\centering
\caption{\textbf{Overlap of disorder and order regions with Pfam domains.}
\textbf{(A)} Number of disorder and order regions with zero and non-zero overlap with any Pfam domain. The proportion of regions with no overlap is significantly greater for the disorder regions ($p < 1 \times 10^{-10}$, chi-squared test). \textbf{(B)} Histogram of the disorder and order regions' overlaps with any Pfam domain. Regions with zero overlap are excluded to more clearly show the distribution.}
\label{sfig:pfam}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=\textwidth]{brownian/out/root.png}
\centering
\caption{\textbf{PCA of disorder regions' feature roots.}
\textbf{(A)} The first two PCs of the disorder regions' feature root distributions. The explained variance percentage of each component is indicated in parentheses in the axis labels. \textbf{(B)} The same plot as panel A with the projections of original variables onto the components shown as arrows. Only the 16 features with the largest projections are shown. Scaling of the arrows is arbitrary.}
\label{sfig:root}
\end{figure}
